---
title: "Constructing identity analysis"
output: html_notebook
author: Colin Tredoux
---

THis document records some work complementing that carried out by Foud and VIAPPL team - constructing identity document. 

# Preliminaries

Load some libraries
```{r loadlibs}
library(pacman)
p_load(tidyverse, psych, lavaan, lavaan.survey, haven, magrittr, nlme,
      stringr, janitor)
devtools::install_github('jtleek/slipper')
library(slipper)
```

Load the data
```{r loaddata, echo=FALSE}

# Some inconsistency in the data structure STILL TO BE REPAIRED
all <- read_spss("data/FINAL 2014 all I and 2G data plus demog_1.sav") %>% 
    clean_names()

# Try reading in file found in Fouads's folder
load("data/2014vpldata2016212.Rdata")

id_equal.dat <- read_spss("data/2014 equal groups indiv and group (1).sav") %>%
    clean_names() %>% 
   mutate(group_condition = ifelse(condition == 0, "individual_equality",
                                   "group_equality"))
id_unequal.dat <- read_spss("data/2014 unequal indiv and group_1 (1).sav") %>% 
    clean_names() %>% 
    mutate(
        group_condition =  case_when(
            condition == 1 ~ "individual_mobility",
            condition == 2 ~ "group_inequality",
            condition == 3 ~ "wealthy_minority"
        )
    )
     
id_all.dat <- full_join(id_equal.dat,id_unequal.dat) %>% 
   clean_names() %>% 
   rename(ingroup_favoritism = igf,
          outgroup_aid = ogg) %>% 
   mutate(equality_cond    = ifelse(str_sub(game_name,1,1) == "E","equality",
                                    "inequality")) %>% 
   mutate(indiv_group_cond =  case_when(
              str_sub(game_name, 2,2) == "I" ~ "individual",
              str_sub(game_name, 2,2) == "M" ~ "wealthy_minority",
              str_sub(game_name, 2,2) ==  1 ~ "group",
              str_sub(game_name, 2,2) ==  2 ~ "group",
              TRUE ~ "not found"
              )
   )
              
  
        
```

Total cases matches that set down by Fouad in the document. 

We need to identify the variables, we do this from the file "Apr17 untrimmed output inequality.txt" which we find in the Dropbox. This tells us the vars for the unequal groups data file.

This tells us that the clustering structure used was gameno, with grouping factor = condition. 

The variables we need are IGF, OGG (OA in the article), rich (status, I think), gameno, ID (pre-id), pID (post-id), deltatokens (I assume the diff between beginning and end of game).

Let's try and construct Fig 1 in the MS

```{r fig1_recon}

mns <- id_all.dat %>% 
    select(group_condition, ingroup_favoritism:outgroup_aid) %>% 
    gather(key = dv, value = amt_given, ingroup_favoritism:outgroup_aid) %>% 
    group_by(group_condition, dv) %>% 
    summarise(mean=mean(amt_given),
              sd = sd(amt_given),
              n = n(),
              ci = (sd/sqrt(n))*1.96)

ggplot(mns, aes(x = group_condition, y = mean, fill = dv))  +
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=mean-ci, ymax=mean+ci),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9)) +
    coord_flip() +
    theme_bw() +
    labs(x = "Group Condition", y = "Mean proportion given over 40 rounds") +
    theme(legend.title = element_blank(), 
          legend.position = c(0.85,0.5))
ggsave("Figure_group_by_giving.pdf")


```

OK, lets try Figure 2 now


```{r fig2_recon}

# Build dataframe that contains standard deviations for conditions
# on Token change and let's bootstrap that a few times to get CIs


id_all.dat %>% 
    group_by(group_condition) %>% 
    summarise(sd = sd(delta_tokens, na.rm = T)/10)

id_all.dat %>% 
    select(group_condition, delta_tokens, uid) %>% 
    spread(key = group_condition, value = delta_tokens) %>% 
    select(-uid) -> x

x %>% summarise_all(funs(sd),na.rm = T)  -> z


x %>% slipper_ci(sd(group_equality, na.rm = T),B=1000) -> group_equality
x %>% slipper_ci(sd(group_inequality, na.rm = T),B=1000) -> group_inequality
x %>% slipper_ci(sd(individual_equality, na.rm = T),B=1000) -> individual_equality
x %>% slipper_ci(sd(individual_mobility, na.rm = T),B=1000) -> individual_mobility
x %>% slipper_ci(sd(wealthy_minority, na.rm = T),B=1000) -> wealthy_minority
group_boot_cis <- full_join(group_equality, group_inequality) %>% 
    full_join(individual_equality) %>% full_join(individual_mobility) %>% 
    full_join(wealthy_minority)

group_boot_cis$group_condition <- c("group_equality", "group_inequality", 
                                    "individual_equality", "individual_mobility",
                                    "wealthy_minority")
group_boot_cis$Standard_deviation <- t(z)

rm(x, group_equality, group_inequality, individual_equality, individual_mobility,
   wealthy_minority, z)

ggplot(group_boot_cis, aes(x = group_condition, y = Standard_deviation))  +
    geom_bar(position=position_dodge(), stat="identity", color="red", 
             fill = "light grey") +
    geom_errorbar(aes(ymin=ci_low, ymax=ci_high),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9)) +
    # coord_flip() +
    theme_bw() +
    labs(x = "",
         y = "Standard deviation of token change over 40 rounds",
         caption = "I bars are bootstrap confidence intervals (1000 samples") 
ggsave("Figure_group_by_sd_token.pdf")


```

Now let's test the sds to see if they differ.  We try the Fligner-Killeen test

```{r cfvariances}
id_all.dat$group_condition <- factor(id_all.dat$group_condition)
fligner.test(delta_tokens ~ group_condition, data=id_all.dat)

(data=id_all.dat %>% filter(group_condition == "group_equality" | 
                            group_condition == "group_inequality") %$%
                            fligner.test(delta_tokens ~ group_condition))
(data=id_all.dat %>% filter(group_condition == "group_equality" | 
                            group_condition == "individual_equality") %$%
                            fligner.test(delta_tokens ~ group_condition))
(data=id_all.dat %>% filter(group_condition == "group_equality" | 
                            group_condition == "individual_mobility") %$%
                            fligner.test(delta_tokens ~ group_condition))
(data=id_all.dat %>% filter(group_condition == "group_equality" | 
                            group_condition == "wealthy_minority") %$%
                            fligner.test(delta_tokens ~ group_condition))
(data=id_all.dat %>% filter(group_condition == "group_inequality" | 
                            group_condition == "individual_equality") %$%
                            fligner.test(delta_tokens ~ group_condition))
(data=id_all.dat %>% filter(group_condition == "group_inequality" | 
                            group_condition == "individual_mobility") %$%
                            fligner.test(delta_tokens ~ group_condition))
(data=id_all.dat %>% filter(group_condition == "group_inequality" | 
                            group_condition == "wealthy_minority") %$%
                            fligner.test(delta_tokens ~ group_condition))
(data=id_all.dat %>% filter(group_condition == "individual_equality" | 
                            group_condition == "individual_mobility") %$%
                            fligner.test(delta_tokens ~ group_condition))
(data=id_all.dat %>% filter(group_condition == "individual_equality" | 
                            group_condition == "wealthy_minority") %$%
                            fligner.test(delta_tokens ~ group_condition))
(data=id_all.dat %>% filter(group_condition == "individual_mobility" | 
                            group_condition == "wealthy_minority") %$%
                            fligner.test(delta_tokens ~ group_condition))

```

There were 10 tests in that, so if we use Bonferroni, then alpha = .005
If so, then the following comparisons are significant
Group equality is smaller than all other conditions
Group inequality is smaller than Individual equality
Group inequality is NOT smaller than Individual mobility
Group inequality is NOT smaller than Wealthy Minority
Indiv equality is smaller than INdiv mobility
INdiv equality is not smaller than wealthy minority
Indiv mobility is not smaller than wealthy minority

We need to check reliability of id measures

```{r check_reliability}

id_all.dat %>% 
    select(id1:id3) %>% 
    omega(nfactors=1)

id_all.dat %>% 
    select(p_id1:p_id3) %>% 
    omega(nfactors=1)

id_all.dat %>% 
    select(id1:id3) %>% 
    summary()
```

Seems good if one looks only at omega and alpha but there is a warning about an unusual case?

Can try the Mixed models test on change in social id over time

```{r check_change}

id_all.dat %>% 
    select(uid, id, p_id, group_condition, gameno) %>% 
    gather(key = time, value = socid, id:p_id) %>% 
    mutate(uid = factor(uid)) -> id_all_lme.dat


a <- lme(socid ~ 1, random = ~1|uid, 
                 data = id_all_lme.dat,
                 na.action = na.omit) 

b <- lme(socid ~ time, random = ~1|uid, 
                 data = id_all_lme.dat,
                 na.action = na.omit) 

c <- lme(socid ~ time, random = ~1|gameno/uid, 
                 data = id_all_lme.dat,
                 na.action = na.omit) 

d <- lme(socid ~ time*group_condition, random = ~1|uid, 
                data = id_all_lme.dat,
                na.action = na.omit,
                method="ML") 

# Re-do model in order to do posthocs
library(lme4)
d <- lmer(socid ~ time*group_condition + (1|uid), 
                data = id_all_lme.dat,
                na.action = na.omit)
d <- lmerTest::lmer(socid ~ time*group_condition + (1|uid), 
                data = id_all_lme.dat,
                na.action = na.omit)
summary(d)
anova(d)
# Look at posthoc tests
library(lsmeans)
# lsmeans(model2way, ~group_space|community) 
# contrast(model2way, method = "eff") 
lsmeans(d, ~time|group_condition)
lsmeans(d, list(pairwise ~ time|group_condition), adjust = "tukey")


    ```

There is an interaction, let's look at the plot

```{r plot_inter}

id_all_lme.dat %>% 
    group_by(group_condition, time) %>% 
    summarise(mean_socid = mean(socid, na.rm = T),
              sd = sd(socid, na.rm = T),
              n= n(),
              ci = (sd/sqrt(n))*1.96) -> id_all_lme_mns.dat

ggplot(id_all_lme_mns.dat, aes(x = group_condition, y = mean_socid, fill = time)) +
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=mean_socid-ci, ymax=mean_socid+ci),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9)) +
    theme_bw() +
    labs(x = "Group Condition", y = "Social Identification") +
    theme(legend.title = element_blank(), 
          legend.position = c(0.80,0.90))
ggsave("Figure_group_by_socid_time.pdf")
 
```





